Hydra Battles and Cie

### 2020-12-07 doc/chapter-powers.tex
corrections of typos

\subsection{The dichotomic strategy}

@@

The efficiency of this method depends on the choice of $b$.
In \cite{DBLP:journals/ita/BrlekCHM95}, the function that maps $n$ into $b$
is called a \emph{strategy}. In this chapter, we concentrate
on the so-called \emph{dichotomic strategy}.

$\delta(n) = n \div {2^k}$ where $k=\floor{(\log_2{n})/2}$.

@@

Module ~\href{../theories/html/hydras.additions.Dichotomy.html}{additions.Dichotomy} contains a definition of the function \texttt{delta}, and proofs that if 
$n>3$ then $1<\delta(n)<n$.

@@

In Sect.~\ref{sect:test-strat}, we compare the three strategies with respect to the lenght of the built chains.

@@

The following function definition generates 9 sub-goals,
for proving that the measure on signatures is strictly decreasing along
the recursive calls. They are solved with the help of Standard Library's lemmas 
on arithemtic of \texttt{positive} numebers end Euclidean division.

@@

\label{sect:test-strat}

@@

\texttt{Recdef}'s \texttt{functional induction} tactic allows us to
prove that every value returned by (\texttt{chain\_gen $s$}) is correct w.r.t. 
\texttt{$s$} and proper.
The proof obligations are solved thanks to the previous lemmas on 
the composition operators on chains: \texttt{Fcompose}, \texttt{KFK}, etc.
Unfortunately, a lot of interaction is still needed or proving properties of
Euclidean division and binary logarithm.

@@

It is now possible to use euclidean addition chains for computing Fibonacci numbers
(see Sections~\vref{sect:fibonacci-mul2} and~\vref{sect:fibonacci-pos-bpow}).

The following function is parameterized by a startegy $\gamma$.

@@

\index{Projects}
\begin{project}
Figures~\vref{fig:F3-as-dag} to \vref{fig:FFK} suggest that any computation following an Euclidean chain can be executed on a kind  of abstract machine with a "register'' and a stack, and only four operations:
\begin{itemize}
\item multiply the contents of the register by the top of the stack (and pop that stack),
\item raising the contents of the register to its square,
\item push the contents of the register into the stack,
\item swapping the two elements at the top of the stack.
\end{itemize}

@@

For instance the chain of Fig.~ \vref{fig:C87} can be represented with the following code:

@@

Please define an Euclidean chain generator using this data structure, and prove its correctness (done  in ~\href{../theories/html/hydras.additions.AM.html}{additions.AM}, but with clumsy fresh proofs). The project is now to simplify the proofs. 
perhaps considering chains of type \texttt{code} as a refinement of functional chains. Please note that many proof scripts are copied verbatim from 
\texttt{Euclidean\_Chains} into \texttt{AM}.
\end{project}

>>>>

\subsection{Generation of chains using Euclidean Dibision}

@@

The efficiency of this method depends on the choice of $b$.
In \cite{DBLP:journals/ita/BrlekCHM95}, the function that maps $n$ into $b$
is called a \emph{strategy}.

\vspace{4pt}
\noindent
From ~\href{../theories/html/hydras.additions.Dichotomy.html}{additions.Dichotomy}.
\begin{Coqsrc}
Class Strategy (gamma : positive -> positive):=
{
gamma_lt :forall p:positive, 3 < p -> gamma  p < p;
gamma_gt : forall p:positive, 3 < p -> 1 < gamma  p
}.

\end{Coqsrc}
\subsection{The dichotomic strategy}

In this chapter, we concentrate
on the so-called \emph{dichotomic strategy}, defined as follows:

$$n \mapsto  n \div {2^k} \,\textbf{where}\, k=\floor{(\log_2{n})/2}$$

@@

This strategy is defined in Module ~\href{../theories/html/hydras.additions.Dichotomy.html}{additions.Dichotomy}.

@@

Page.~\pageref{sect:test-strat}, we compare the three strategies with respect to the length of the built chains.

@@

The following function definition generates 9 sub-goals,
for proving that the measure on signatures is strictly decreasing along
the recursive calls. They are solved with the help of Standard Library's lemmas 
on arithmetic of \texttt{positive} numbers and Euclidean division.

@@

\subsubsection{A few tests}
\label{sect:test-strat}

@@

\texttt{Recdef}'s \texttt{functional induction} tactic allows us to
prove that every value returned by (\texttt{chain\_gen $s$}) is correct w.r.t. 
\texttt{$s$} and proper.
The proof obligations are solved thanks to the previous lemmas on 
the composition operators on chains: \texttt{Fcompose}, \texttt{KFK}, etc.
Unfortunately, a lot of interaction is still needed for proving properties of
Euclidean division and binary logarithm.

@@

It is now possible to use Euclidean addition chains for computing Fibonacci numbers
(see Sections~\vref{sect:fibonacci-mul2} and~\vref{sect:fibonacci-pos-bpow}).

The following function is parameterized by any strategy $\gamma$.

@@

\subsection{A data structure for Euclidean chains}

Figures~\vref{fig:F3-as-dag} to \vref{fig:FFK} suggest that any computation following an Euclidean chain can be executed on a kind  of abstract machine with a "register'' and a stack, and only four operations:
\begin{itemize}
\item multiply the contents of the register by the top of the stack (and pop that stack),
\item raising the contents of the register to its square,
\item push the contents of the register into the stack,
\item swapping the two elements at the top of the stack.
\end{itemize}

@@

For instance the chain of Fig.~\vref{fig:C87} can be represented with the following code:

@@

In the library~\href{../theories/html/hydras.additions.AM.html}{additions.AM},
we define a chain generator for this data structure. 
Please note that many proof scripts are copied verbatim from 
\texttt{Euclidean\_Chains} into \texttt{AM}. Removing such redundancies is left as a project.
